On the reality of the quantum state once again

### 2021-12-09 Articles/2021-HarriganSpekkens/HarriganSpekkens.tex
HarriganSpekkens: minor changes

Suppose we have two preparation devices, one that prepares z+ and another that prepares z-, and we toss a fair coin to choose which one to use. This results into an epistemic state with equal distribution on z+ and z-. Now suppose we have two additional preparation devices, this time for x+ and x-, and we again toss a fair coin. This time we have an epistemic state with equal distribution on x+ and x-. Note that the epistemic distributions do not overlap. Therefore, according to the HS categorization, these correspond to two ontologically distinct states, making the preparation axis an ontological property of the system, regardless of the orientation. However, in terms of density matrixes both these situations would not just overlap: they would be represented by the same maximally mixed state. Hence there seems to be a mismatch between the type of epistemic knowledge one can express in quantum mechanics through mixed states and the type of epistemic knowledge described in the HS model. This needs to be investigated further.

>>>>

Suppose we have two preparation devices, one that prepares z+ and another that prepares z-, and we toss a fair coin to choose which one to use. This results into an epistemic state with equal distribution on z+ and z-. Now suppose we have two additional preparation devices, this time for x+ and x-, and we again toss a fair coin. This time we have an epistemic state with equal distribution on x+ and x-. Note that the epistemic distributions do not overlap. Therefore, according to the HS categorization, these correspond to two ontologically distinct states, making the preparation axis an ontological property of the system, regardless of the orientation. However, in terms of density matrixes both these situations would not just overlap: \emph{they would be represented by the same maximally mixed state.} Hence there seems to be a mismatch between the type of epistemic knowledge one can express in quantum mechanics through mixed states and the type of epistemic knowledge described in the HS model. This needs to be investigated further.
